---
title: "Determing the analyses to run for MR-EvE"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{setup_inventory}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mrever)
```

The MR-EvE surface of results needs to be generated on a set of data, and then updated as new analyses come in. Ideally each ID will be treated as a separate batch to enable simple parallelisation. Further parallelisation can be performed within the batch using multi-core functions when necessary.

To avoid having to re-run everything each time, we would like to be able to determine what new analyses need to be run given knowledge of the existing list of dataset IDs, and a list of new dataset IDs. 

For MR-EvE our objective is to ultimately have a test of every trait against every other trait (bi-directional exhaustive MR).

## Initialising

When running for the first time, if there are $N$ traits, we will perform $N^2 - N$ analyses (excluding the diagonal). This can be split into $N$ batches. Each batch performs only the tests in which its ID is the exposure. For example, if there are 10 IDs `1,2,...,10` then here are the analyses that ID `1` will run:

```{r}
determine_analyses(id=1, idlist=1:10)
```

and here are the ones that ID `2` will run:

```{r}
determine_analyses(id=2, idlist=1:10)
```

and so on. We can see we get the right number of tests using this approach. Expected number of tests:

```{r}
10 * 10 - 10
```

Number of tests:

```{r}
tests <- lapply(1:10, function(x) determine_analyses(x, 1:10)) %>% dplyr::bind_rows()
nrow(tests)
length(unique(tests$id))
```

## Adding new datasets

Once the initial space is created, adding new datasets is a bit more complicated. If we have $M$ new analyses, ideally we would only run $M$ new batches. If we only ran the exposure analses for each of the $M$ IDs then we would get the estimate of every $M$ on every $M + N$, but we would not get any estimates of $N$ on $M$. So we actually need to run 

- Exposure of $M$ on $M + N$
- Exposure of $N$ on $M$

For example, now we add two new IDs `11, 12`.


```{r}
determine_analyses(id=11, idlist=1:10, newidlist=11:12) %>% as.data.frame
```

We now expect the following number of tests in total:

```{r}
12 * 12 - 12
```

Check:

```{r}
tests1 <- lapply(1:10, function(x) determine_analyses(x, 1:10)) %>% dplyr::bind_rows()
tests2 <- lapply(11:12, function(x) determine_analyses(x, 1:10, 11:12)) %>% dplyr::bind_rows()
tests <- dplyr::bind_rows(tests1, tests2)
nrow(tests)
length(unique(tests$id))
```


